---
title: "Rap"
author: "Benjamin Gramza"
date: "4/14/2020"
output: html_document
---


```{r Read in Data}
library(tidyverse)
library(plotly)
library(RColorBrewer)
polls <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-14/polls.csv')
rankings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-14/rankings.csv')
```
```{r}
BensTheme <- theme_bw() + 
  # Dark Theme
  theme(plot.background = element_rect(fill = "black")) + 
  # Change plot title color 
  theme(plot.title = element_text(color = "goldenrod"))+
  # Change the colors of plot panel background to lightblue
  # and the color of grid lines to white
  theme(
  panel.background = element_rect(fill = "white",
                                colour = "goldenrod",
                                size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "grey50"), 
  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "grey90"),
  panel.border = element_rect(colour = "goldenrod",fill=NA,size = 2),
  text = element_text(family="sans",colour = "goldenrod",face="bold"),
  axis.text = element_text(size = rel(.8), face="bold", colour = "white"),
  legend.position = "none")
```
```

```{r}
df <- rankings %>% select(artist,title,points,year)%>%
  group_by(year) %>% top_n(1, points)
df$Song <- paste0(df$title," - ",df$artist)
plot <- ggplot(data=df,mapping = aes(x=year,y=points,label=Song,fill=points))+
  geom_col()+
  scale_fill_gradient(low="black",high = "red")+
  ggtitle("Highest Ranked Rap Song by Year")+
  labs(x = "Year",
       y = "Ranking Points")+
  BensTheme +
     annotate("text", x = Inf, y = -Inf, label = "GramzaStats",
            hjust=1.1, vjust=-8.5, col="grey80", cex=6,
            fontface = "bold", alpha = 0.8)
  
plot

plotly <- ggplotly(plot,tooltip=c("x","y","label"))
plotly
```

